Analysis of Global Crises and Their Impact on Interational Well-Being

### 2024-11-15 Draft.Rmd
Update Draft.Rmd

The analysis highlighted an interesting finding, as shown in @ref(fig ): a significant concentration of COVID-19 cases appears within the 1500-2500 km range from the equator, suggesting a strong relationship between COVID-19 cases and cyclone activity within a margin of approximately 9 degrees of longitude. This area also highlights a geographical strip pointing to a genreal trend of lower GDP, government stability, and overall happiness.

```{r insight1, fig.cap="This is a figure caption that you will need to change in order to get good marks in the visualization rubric items."}

@@

```{r}
#Social support & life ladder

>>>>

The analysis highlighted an interesting finding, as shown in \@ref(fig:insight1): a significant concentration of COVID-19 cases appears within the 1500-2500 km range from the equator, suggesting a strong relationship between COVID-19 cases and cyclone activity within a margin of approximately 9 degrees of longitude. This area also highlights a geographical strip pointing to a genreal trend of lower GDP, government stability, and overall happiness.

```{r insight1, fig.cap=""}

@@

```{r insight2, fig.cap=""}
#Social support & life ladder
